Computable Compressed Matrices\\Suplementary Material

### 2013-09-25 plos.tex
Introdução e método SM analisados.

@@

In this paper we present two methods that allow the compression of large data sets, such as the type of big data, for direct manipulation of files into memory. These methods allow direct access to data in compressed form, its handling and recovery occurs without loss. The proposed method also allows to use the techniques already presented to perform a subsequent compression process only if these data should be stored on physical media. We describe the process of compression and decompression, using as an example strips of bits to represent numerical arrays, the method sparse string \cite{salomon,salomon2}, to illustrate the methods. We also present a discussion of some results on the characteristics of each proposed method and elucidated the best options in which each can be applied. We have also emphasized that the methods allow information to be accessed after the compression process, which allows the handling and updating, if necessary. At the end of the paper we present their conclusions about using of 
the proposed methods.

@@

To check the efficiency of these methods, we consider that this matrix is composed of numbers generated from random variables that follow a probability distributions mixture.

>>>>

\usepackage[colorinlistoftodos]{todonotes}

@@

In this paper, we present two methods that allow the compression of large data 
sets, such as the type of big data, for direct manipulation of files into 
memory. These methods allow direct access to data in compressed form, its 
handling and recovery occurs without loss. The proposed method also allows to 
use the techniques already presented to perform a subsequent compression process 
only if these data should be stored on physical media. We describe the process 
of compression and decompression, using as an example strips of bits to 
represent numerical arrays, the method sparse string \cite{salomon,salomon2}, to 
illustrate the methods. We also present a discussion of some results on the 
characteristics of each proposed method and elucidated the best options in which 
each can be applied. We have also emphasized that the methods allow information 
to be accessed after the compression process, which allows the handling and 
updating, if necessary. At the end of the paper we present their conclusions 
about using of the proposed methods.

@@

To check the efficiency of these methods, at first, we consider that this 
matrix is composed of numbers generated from random variables that follow a 
probability distributions mixture.
